Updates on the Exoplanet Orbit Database

### 2014-03-04 draft/ms.tex
Orbital parameters section done

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}

@@

ZZZ For KOIs without MSINI measured, we import the MASS fields from the Exoplanet Archive, which are derived from the mass-radius relation in .

@@

%------------------------------------------------------------------------------
\subsection{Transit Parameters}
We report the transit parameters of transiting planets. These parameters are available only when the planet has TRANSIT flag equal to 1. 
Added fields since \cite{Wright2011}:

{\bf DR} is the distance between the planet and the star during the transit in stellar radii. This is one of the parameters that goes into the transit light curve modeling and for more information, see Batalha 2013 for more details.

{\bf RR} is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
Why did we add this field?

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rearth{R_\oplus}

@@

ZZZ For KOIs without MSINI measured, we calculate their mass using the mass-radius relation from the literatures. For KOIs with $R<4\rearth$, we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use \cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use \cite{Mordasini2012}.

@@

%------------------------------------------------------------------------------
\subsection{Transit Parameters}
We report the transit parameters, which are available only when the planet has TRANSIT flag equal to 1. We describe added fields since \cite{Wright2011} below.

{\bf DR} is the distance between the planet and the star during the transit in stellar radii. This is one of the parameters that goes into the transit light curve modeling (see e.g. \citealt{Batalha2013}).

{\bf RR} is the ratio of the planetary radius and the stellar radius. If the transit depth (DEPTH) is not given, we calculate DEPTH by taking square of RR but we do not calculate RR from DEPTH.
